An HPSG account for deliminative verbal reduplication in Mandarin Chinese

### 2024-08-18 main.tex
Update 2024-08-18-17:19:01

\rightrunning{An HPSG account for verbal reduplication in Mandarin Chinese} % Short title

\title{An HPSG account for verbal reduplication in Mandarin Chinese}

@@

\begin{abstract}
The current study presents an HPSG analysis for verbal reduplication in Mandarin Chinese. We provide a detailed description of the phenomenon. After discussing reduplication’s interaction with \textit{Aktionsarten} and aspect markers, we argue that it is a morphological rather than a syntactic process. We put forward a lexical rule for verbal reduplication in Mandarin Chinese, and the different forms of reduplication are captured in an inheritance hierarchy. The interaction between verbal reduplication and aspect marking is handled by multiple inheritance. This analysis covers all forms of verbal reduplication in Mandarin Chinese and has none of the shortcomings of previous analyses.
\keywords{verbal reduplication, Mandarin Chinese, HPSG, Minimal Recursion Semantics}
\end{abstract}

>>>>

\rightrunning{An HPSG account for deliminative verbal reduplication in Mandarin Chinese} % Short title

\title{An HPSG account for deliminative verbal reduplication in Mandarin Chinese}

@@

\begin{abstract}
The current study presents an HPSG analysis for deliminative verbal reduplication in Mandarin Chinese. We provide a detailed description of the phenomenon. After discussing reduplication’s interaction with \textit{Aktionsarten} and aspect markers, we argue that it is better analyzed as a morphological rather than a syntactic process. We put forward a lexical rule for verbal reduplication in Mandarin Chinese, and the different forms of reduplication are captured in an inheritance hierarchy. The interaction between verbal reduplication and aspect marking is handled by multiple inheritance. This analysis covers all forms of deliminative verbal reduplication in Mandarin Chinese and has none of the shortcomings of previous analyses.
\keywords{verbal reduplication, Mandarin Chinese, HPSG, Minimal Recursion Semantics}
\end{abstract}
